---
title: "Weight of Fish"
author: "Brooke De La Torre"
date: "11/4/2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fishdata=read.csv("Fish.csv",header = TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

We are trying to explain if weight has a difference based on their length and width through the use of graphs. 

$H_0$:There is a difference in weight caused by length, width, or height. 

$H_A$:There is no difference in weight caused by length, width, or height. 

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We are using a numerical~numerical because all of the variables we are looking at are all numerical explanatory variables. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
FishiesP=filter(Fishdata, Species == "Perch")
FishiesP = select(FishiesP,-(Species))
pairs(FishiesP)
```

As the graph shows the Length 2 and the width show the most linearity.

```{r}
FishiesB=filter(Fishdata, Species == "Bream")
FishiesB = select(FishiesB,-(Species))
pairs(FishiesB)
```

As the graph shows the Length 2 and the height show the most linearity.

```{r}
FishiesS=filter(Fishdata, Species == "Smelt")
FishiesS = select(FishiesS,-(Species))
pairs(FishiesS)
```

As the graph shows the Length 2 and the height show the most linearity.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
summary(FishiesP)
```
  
The summary of the Perch data shows that all lengths have a min around 8 and a median around 23. All quartiles are in the same range of eachother for the lengths. 
  
```{r}
summary(FishiesB)
```

The summary of the Breech data shows numerical data of a box and whisker plot. It shows the minimum, median, and mean of each numerical data set broken up.

```{r}
summary(FishiesS)
```

The summary of the Smelt data shows numerical data of a box and whisker plot. It shows the minimum, median, and mean of each numerical data set broken up.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesP,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesB,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesS,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
Perchmodel=lm(Weight~Height+Width,data=FishiesP)
summary(Perchmodel)
```

```{r}
Breammodel=lm(Weight~Length2+Height,data=FishiesB)
summary(Breammodel)
```

```{r}
Smeltmodel=lm(Weight~Length2+Height,data=FishiesS)
summary(Smeltmodel)
```
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
